### 2016-03-11 paper/abstract.tex

\begin{abstract}
This paper proposes a novel MAP inference framework for Markov Random
Field (MRF) problems in parallel computing environments.  The inference
framework, dubbed Swarm Fusion method, is a natural generalization of
the Fusion Move method. Every thread (in a case of multi-threading
environments) maintains and updates a solution. At every iteration, a
thread can generate arbitrary number of solution proposals and take
arbitrary number of concurrent solutions from the other threads to
perform multi-way fusion in updating its solution. The framework is
general, making popular existing inference techniques such as
alpha-expansion, fusion move, parallel alpha-expansion, or hierarchical
fusion, its special cases. We have evaluated the effectiveness of our
approach against competing methods on three problems of varying
difficulties, in particular, the stereo, the optical flow, and the
layered depthmap estimation problems.
%Our experiments have shown that the Swarm Fusion method outperform
%competing methods, especially for challenging problems with massive
%solution space.
% can effectively exploits the parallel computing resources and become
%effective especially for challenging problems.
%\yasu{must be at least 70 and at most 150 words.}
\keywords{MRF; Fusion Move; Particle Swarm Optimization}
\end{abstract}

>>>>

\begin{abstract}
This paper proposes a novel MAP inference framework for Markov Random
Field (MRF) in parallel computing environments.  The inference
framework, dubbed Swarm Fusion, is a natural generalization of the
Fusion Move method. Every thread (in a case of multi-threading
environments) maintains and updates a solution. At every iteration, a
thread can generate arbitrary number of solution proposals and take
arbitrary number of concurrent solutions from the other threads to
perform multi-way fusion in updating its solution. The framework is
general, making popular existing inference techniques such as
alpha-expansion, fusion move, parallel alpha-expansion, or hierarchical
fusion, its special cases. We have evaluated the effectiveness of our
approach against competing methods on three problems of varying
difficulties, in particular, the stereo, the optical flow, and the
layered depthmap estimation problems.
%Our experiments have shown that the Swarm Fusion method outperform
%competing methods, especially for challenging problems with massive
%solution space.
% can effectively exploits the parallel computing resources and become
%effective especially for challenging problems.
%\yasu{must be at least 70 and at most 150 words.}
\keywords{MRF; Fusion Move; Particle Swarm Optimization}
\end{abstract}

### 2016-03-11 paper/conclusion.tex

\section{Conclusion and future direction}
We have proposed a novel MAP inference framework, Swarm Fusion, for MRF
problems in parallel computing environments. The framework is general,
and we showed that most popular inference techniques such as
alpha-expansion, Fusion Move, parallel alpha-expansion, or hierarchical
fusion, are its special cases. Our experiments have revealed that the
framework exploits parallel computational resources and achieves faster
convergence, epseically for challenging problems.  Our first future work
is to conduct experiments on cloud computing environments, in
particular, the MapReduce programming model, where the roles of mappers
and reducers exactly correspond to the processes of parallel multi-way
fusion and solution exchanges, respectively.  Another future work is the
automatic configuration of the Swarm Fusion architecture. Due to its
vast degrees of freedom, one needs to currently hand-tune the
architecture for the optical performance. An interesting direction is to
adaptively change its architecture during the computation, for example,
switching to simple parallel alpha-expansion for easy problems, or
increasing the rate of solution exchanges when solutions vary
significantly across threads.
%
Parallel MAP inference has been a relatively under-explored topic in
Computer Vsion. Our idea is very simple and adapting the Swarm Fusion
framework require minimal coding. We believe that this paper has a
potential to immediately benefit tens of thousands of Computer Vision
researchers or engineers in the world, who currently solve MRF problems
with conventional solvers. We will share our source code and the
datasets with the community.

>>>>

\section{Conclusion and future directions}
We have proposed a novel MRF inference framework, Swarm Fusion, in
parallel computing environments. The framework is general and makes
popular inference techniques such as Alpha Expansion, Fusion Move,
Parallel Alpha Expansion, or Hierarchical Fusion, its special cases. Our
experiments have revealed that the framework exploits parallel
computational resources and achieves faster convergence, epseically for
challenging problems.  Our first future work is to conduct experiments
on cloud computing environments, in particular, the MapReduce
programming model, where the roles of mappers and reducers exactly
correspond to the processes of parallel multi-way fusion and solution
sharing, respectively.  Another future work is the automatic
configuration of the Swarm Fusion architecture.  Our experiments have
shown that optimal architectures are different for different problems.
An interesting direction is to adaptively change its architecture during
the computation, for example, switching to simple parallel
alpha-expansion for easy problems, or increasing the rate of solution
exchanges when solutions vary significantly across threads.
%
Parallel MRF inference has been a relatively under-explored topic in
Computer Vsion. Our idea is very simple, where adapting the Swarm Fusion
framework require minimal coding. We believe that this paper would
immediately benefit tens of thousands of Computer Vision researchers or
engineers in the world, who currently solve MRF problems. We will share
our source code and the datasets with the community.

### 2016-03-11 paper/introduction.tex

\section{Introduction}
Parallel computation has changed the field of computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computational nodes
in a cloud.
%
In the recent work on the AI program playing the ancient Chinese board
game of {\it Go} (AlphaGo from DeepMind), parallelization plays a key
role in the Monte-Carlo tree search~\cite{nature_alpha_go}.

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs~\cite{canon?}, stitch thousands of images to generate gigapixel
panoramas~\cite{gigapan}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{Joint3DSceneReconstructionandclassSegmentation}.
%
%
However, state-of-the-art algorithms are still inherently sequential in
many Computer Vision problems. Take a Fusion Move method
(FM)~\cite{viktor,second_order_stereo,else}, which has been one of the
most effective techniques for the Markov Random Field (MRF) inference,
for example~\cite{fusion_moves}.
%
It sequentially improves solution by fusing the current solution with a
solution proposal. Its successful applications range from optical flow,
stereo, image denoising, image inpainting, to image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.

@@

We have evaluated the effectiveness of our approach over three problems
in Computer Vision, stereo, optical flow, and layered
depthmap estimation.
%
%Our approach outperforms all the other competing methods, especially for
%challenging problems with a large label space.
Our idea is very simple and the method is easily reproducible with
minimal coding.
% will instantly benefit every Computer Vision researcher or
% engineer, who currently uses fusion move algorithm on multi-core
% environments to solve challenging problems.
% We will share our implementation of the algorithm.

>>>>

\section{Introduction}
Parallel computation has changed the field of computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computational nodes
in a cloud.
%
In the recent work on the AI program playing the ancient Chinese board
game of {\it Go}, parallelization plays a key role in the Monte-Carlo
tree search~\cite{nature_alpha_go}.

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs (e.g., Canon EOS 5DS), stitch thousands of images to generate gigapixel
panoramas~\cite{gigapan}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{Joint3DSceneReconstructionandclassSegmentation}.
%
%
However, state-of-the-art algorithms are still inherently sequential in
many Computer Vision problems. Take a Fusion Move method
(FM)~\cite{viktor,second_order_stereo,else} for example, which has been
one of the most effective techniques for Markov Random Field (MRF)
inference, including the above problems like image denoising, image
stitching, or volumetric reconstruction.
%
It sequentially improves solution by fusing the current solution with a
solution proposal. Its successful applications go beyond and also cover
optical flow, stereo, image inpainting, or image segmentation
problems~\cite{fusion_moves_for_markov_random_field_optimization}.

@@

We have evaluated the effectiveness of our approach over three problems
in Computer Vision, stereo, optical flow, and layered
depthmap estimation.
%
%Our approach outperforms all the other competing methods, especially for
%challenging problems with a large label space.
Our idea is very simple. We believe that the method is easily
reproducible with minimal coding, and would have immediate impact on
numerous Computer Vision researchers or engineers, who currently solve
MRF problems.
% will instantly benefit every Computer Vision researcher or
% engineer, who currently uses fusion move algorithm on multi-core
% environments to solve challenging problems.
% We will share our implementation of the algorithm.

### 2016-03-11 paper/stereo.tex

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this stereo
represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average Normalized Cross Correlation
score between the reference image and the others inside a $7\times 7$
pixels window. Pairwise terms are simple Pottz model. The total energy
is defined by the sum of the two, while scaling the pairwise term by a
factor of \yasu{X value}.
%
We use Middlebury stereo datasets for the experiments.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
For SF-SS, we have chosen $\alpha=2$ ($\beta=0$). For SF-MF, each thread
iterates the step of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so
that it can take a solution proposal in one step and a neighboring
solution in the next. For the standard SF, we have used ($\alpha=1, \beta=1$).
%
%
%
%
To make the comparison simple, we restrict our proposal
generation to be constant-label proposals. Graph-cuts is used in fusing
a constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.

>>>>

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this stereo
represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average Normalized Cross Correlation
score between the reference image and the others inside a $7\times 7$
pixels window. Pairwise terms are simple Pottz model. The total energy
is defined by the sum of the two, while scaling the pairwise term by a
factor of \yasu{X value}.
%
We use images from the Middlebury stereo benchmark~\cite{middlebury_stereo}.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
2. SF-MF implies $\alpha+\beta=1$, where each thread iterates the step
of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so that it can take a
solution proposal in one step and a neighboring solution in the
next. For standard SF, we have used ($\alpha=1, \beta=1$).
%
%
%
%
To make the comparison simple, we restrict our proposal
generation to be constant-label proposals. Graph-cuts is used in fusing
a constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
